---
title: "pml project"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r}
MyData <- read.csv(file="pml.csv")
dim(MyData)
str(MyData)
head(MyData)
summary(MyData)
table(is.na(MyData))
colSums(is.na(MyData))
library(dplyr)
library(ggplot2)
##remove N/A
train<- MyData[ , colSums(is.na(MyData)) == 0]
train$classe<- as.numeric(train$classe)
str(train)
summary(train)
#subset<-   roll_belt        pitch_belt          yaw_belt       total_accel_belt   gyros_belt_x        gyros_belt_y       gyros_belt_z      accel_belt_x 
#accel_belt_y     accel_belt_z  roll_arm         pitch_arm   magnet_belt_x   magnet_belt_y   magnet_belt_z     
#yaw_arm          total_accel_arm  gyros_arm_x        gyros_arm_y       gyros_arm_z       
a<-select_if(train, is.numeric)
str(a)
summary(a)
a <- a[-(1)]
model<- lm(classe~. ,data = a)
summary(model)
#select Coefficients ***
b<-subset(a, select=-c(raw_timestamp_part_2,num_window,gyros_belt_x,magnet_belt_x,roll_arm,gyros_arm_z,accel_dumbbell_z,yaw_forearm,gyros_forearm_y,gyros_forearm_z,magnet_forearm_z))
#b cut to training testing cross
library(caret)
intrain<-createDataPartition(y=b$classe,p=0.7,list=FALSE)
training<-b[intrain,]
testing<-b[-intrain,]
test<-testing
crossv<-createDataPartition(y=test$classe,p=0.5,list=FALSE)
testing<-test[crossv,]
crossing<-test[-crossv,]
training$classe<- as.factor(training$classe)
#train with rf
set.seed(0215)
mod1<-train(classe~.,method="rpart",data = training)
#predict on test
crossing$classe<- as.factor(crossing$classe)
pred1 <- predict(mod1,crossing)
pred1df<-data.frame(pred1,crossing$classe)
summary(pred1df)
table(pred1df$pred1,crossing$classe)
#0.49
mod2<-train(classe~.,method="gbm",data = training)
pred2 <- predict(mod2,crossing)
pred2df<-data.frame(pred2,crossing$classe)
summary(pred2df)
table(pred2df$pred2,crossing$classe)
#0.99 test accuacry
#use mod 2 to predict testing
testing1<-testing[,1:44]
predt <- predict(mod2,testing1)
predtdf<-data.frame(predt,testing$classe)
summary(predtdf)
table(predtdf$predt,testing$classe)
#0.99 out sample accuacry
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
